---
title: "Split Packed Bubble Plot"
author: "Jorge Bris Moreno"
format:
  html:
    embed-resources: true
    toc: true
editor_options:
  chunk_output_type: console
execute:
  echo: false
--- 

```{r, echo=FALSE, results='asis', runtime="js"}
# Calling highcharts
cat('
<script src="https://code.highcharts.com/maps/highmaps.js"></script>
<script src="https://code.highcharts.com/maps/modules/exporting.js"></script>
<script src="https://code.highcharts.com/maps/modules/accessibility.js"></script>
')
```

```{r, message=FALSE, warning=FALSE, eval=FALSE}
# Load necessary libraries
library(dplyr)
library(jsonlite)

# Read data from CSV
data <- read.csv("cleaned_data/filtered_education_data.csv")
```

```{r, message=FALSE, warning=FALSE, eval=FALSE}
head(data)
```

```{r, message=FALSE, warning=FALSE, eval=FALSE}
library(dplyr)
library(jsonlite)

indicators <- c("Gross enrolment ratio, primary, female (%)",
                "Gross enrolment ratio, secondary, female (%)",
                "Gross enrolment ratio, tertiary, female (%)")

save_json_by_indicator <- function(indicator_name) {
  filtered_data <- data %>%
    filter(Indicator.Name == indicator_name, !is.na(X2014)) %>%
    mutate(name = Country.Code, value = X2014) %>%
    select(name, value) %>%
    filter(!name %in% c("Arab World", "East Asia & Pacific", "East Asia & Pacific (excluding high income)", "Euro area", "Europe & Central Asia", "Europe & Central Asia (excluding high income)", "European Union", "Heavily indebted poor countries (HIPC)", "High income", "Latin America & Caribbean", "Latin America & Caribbean (excluding high income)", "Low & middle income", "Low income", "Lower middle income", "Middle East & North Africa", "Middle East & North Africa (excluding high income)", "Middle income", "North America", "OECD members", "South Asia", "Sub-Saharan Africa", "Sub-Saharan Africa (excluding high income)", "Upper middle income", "World", "Least developed countries: UN classification"))

  if (nrow(filtered_data) > 0) {
    json_data <- toJSON(filtered_data, pretty = TRUE)
    file_name <- paste0("Jorge_Plot/data/", gsub("[, %]", "", gsub(" ", "_", indicator_name)), ".json")
    write(json_data, file = file_name)
    return(paste("Data written to", file_name, "with", nrow(filtered_data), "records"))
  } else {
    return(paste("No data found for", indicator_name))
  }
}

results <- lapply(indicators, save_json_by_indicator)
results
```

::: {.panel-tabset}

## Primary Ed.

```{ojs}
colorPalette = [
  [0, '#330f63'],    // dark blue-purple
  [0.1, '#481567'],  // deep purple
  [0.2, '#5f1868'],  // deep purple
  [0.3, '#76216b'],  // dark purple
  [0.4, '#8f2769'],  // dark purple-pink
  [0.5, '#ab3e5b'],  // purplish red
  [0.6, '#c7584c'],  // red-orange
  [0.7, '#e1793e'],  // orange
  [0.8, '#f5a234'],  // bright orange
  [0.9, '#f9c957'],  // yellow-orange
  [1, '#fcffa4']     // very light yellow
];

data1 = [
  {
    "name": "ARB",
    "value": 93.608
  },
  {
    "name": "EAS",
    "value": 104.9668
  },
  {
    "name": "EAP",
    "value": 105.2243
  },
  {
    "name": "EMU",
    "value": 103.4798
  },
  {
    "name": "ECS",
    "value": 103.1583
  },
  {
    "name": "ECA",
    "value": 101.6871
  },
  {
    "name": "EUU",
    "value": 103.9449
  },
  {
    "name": "HPC",
    "value": 98.0805
  },
  {
    "name": "HIC",
    "value": 102.0787
  },
  {
    "name": "LCN",
    "value": 107.0963
  },
  {
    "name": "LAC",
    "value": 107.3809
  },
  {
    "name": "LDC",
    "value": 100.2302
  },
  {
    "name": "LMY",
    "value": 104.3708
  },
  {
    "name": "LIC",
    "value": 99.2115
  },
  {
    "name": "LMC",
    "value": 105.5588
  },
  {
    "name": "MEA",
    "value": 103.047
  },
  {
    "name": "MNA",
    "value": 102.4904
  },
  {
    "name": "MIC",
    "value": 105.0638
  },
  {
    "name": "NAC",
    "value": 99.3733
  },
  {
    "name": "OED",
    "value": 102.2592
  },
  {
    "name": "SAS",
    "value": 112.5074
  },
  {
    "name": "SSF",
    "value": 94.7694
  },
  {
    "name": "SSA",
    "value": 94.7689
  },
  {
    "name": "UMC",
    "value": 104.2601
  },
  {
    "name": "WLD",
    "value": 103.8494
  },
  {
    "name": "AFG",
    "value": 91.7579
  },
  {
    "name": "ALB",
    "value": 111.1673
  },
  {
    "name": "DZA",
    "value": 115.1333
  },
  {
    "name": "ATG",
    "value": 93.3092
  },
  {
    "name": "ARG",
    "value": 109.7614
  },
  {
    "name": "ABW",
    "value": 115.4297
  },
  {
    "name": "AUS",
    "value": 105.7587
  },
  {
    "name": "AUT",
    "value": 101.6984
  },
  {
    "name": "AZE",
    "value": 105.493
  },
  {
    "name": "BHR",
    "value": 100.456
  },
  {
    "name": "BRB",
    "value": 94.1669
  },
  {
    "name": "BLR",
    "value": 99.0571
  },
  {
    "name": "BEL",
    "value": 104.9222
  },
  {
    "name": "BLZ",
    "value": 108.95
  },
  {
    "name": "BEN",
    "value": 119.9226
  },
  {
    "name": "BMU",
    "value": 86.0617
  },
  {
    "name": "BTN",
    "value": 102.8738
  },
  {
    "name": "BOL",
    "value": 95.8438
  },
  {
    "name": "BWA",
    "value": 105.8012
  },
  {
    "name": "BRA",
    "value": 108.9931
  },
  {
    "name": "BRN",
    "value": 107.5561
  },
  {
    "name": "BGR",
    "value": 98.7499
  },
  {
    "name": "BFA",
    "value": 85.0913
  },
  {
    "name": "BDI",
    "value": 128.4259
  },
  {
    "name": "CPV",
    "value": 109.907
  },
  {
    "name": "KHM",
    "value": 113.1353
  },
  {
    "name": "CMR",
    "value": 106.885
  },
  {
    "name": "CHL",
    "value": 98.8515
  },
  {
    "name": "CHN",
    "value": 104.0123
  },
  {
    "name": "COL",
    "value": 111.7424
  },
  {
    "name": "COM",
    "value": 99.4594
  },
  {
    "name": "COD",
    "value": 101.8445
  },
  {
    "name": "CRI",
    "value": 110.286
  },
  {
    "name": "CIV",
    "value": 83.5878
  },
  {
    "name": "HRV",
    "value": 98.7139
  },
  {
    "name": "CUB",
    "value": 95.8327
  },
  {
    "name": "CYP",
    "value": 99.5871
  },
  {
    "name": "CZE",
    "value": 98.8783
  },
  {
    "name": "DNK",
    "value": 100.6596
  },
  {
    "name": "DJI",
    "value": 63.263
  },
  {
    "name": "DMA",
    "value": 117.9919
  },
  {
    "name": "DOM",
    "value": 95.7246
  },
  {
    "name": "ECU",
    "value": 113.4911
  },
  {
    "name": "EGY",
    "value": 103.7742
  },
  {
    "name": "SLV",
    "value": 109.7239
  },
  {
    "name": "ERI",
    "value": 47.1461
  },
  {
    "name": "EST",
    "value": 99.0226
  },
  {
    "name": "ETH",
    "value": 95.8226
  },
  {
    "name": "FIN",
    "value": 101.3999
  },
  {
    "name": "FRA",
    "value": 104.971
  },
  {
    "name": "GMB",
    "value": 90.8281
  },
  {
    "name": "GEO",
    "value": 117.5432
  },
  {
    "name": "DEU",
    "value": 102.9817
  },
  {
    "name": "GHA",
    "value": 106.4023
  },
  {
    "name": "GRC",
    "value": 97.1059
  },
  {
    "name": "GRD",
    "value": 102.2528
  },
  {
    "name": "GTM",
    "value": 101.5921
  },
  {
    "name": "GIN",
    "value": 83.7966
  },
  {
    "name": "HND",
    "value": 108.0323
  },
  {
    "name": "HUN",
    "value": 100.9149
  },
  {
    "name": "IND",
    "value": 114.0863
  },
  {
    "name": "IDN",
    "value": 104.4599
  },
  {
    "name": "IRN",
    "value": 111.5957
  },
  {
    "name": "IRL",
    "value": 102.5718
  },
  {
    "name": "ISR",
    "value": 104.3748
  },
  {
    "name": "ITA",
    "value": 101.0766
  },
  {
    "name": "JPN",
    "value": 101.1876
  },
  {
    "name": "JOR",
    "value": 97.6112
  },
  {
    "name": "KAZ",
    "value": 111.3404
  },
  {
    "name": "KEN",
    "value": 111.5768
  },
  {
    "name": "KIR",
    "value": 115.182
  },
  {
    "name": "KOR",
    "value": 98.5283
  },
  {
    "name": "KWT",
    "value": 103.025
  },
  {
    "name": "KGZ",
    "value": 107.0264
  },
  {
    "name": "LAO",
    "value": 113.4927
  },
  {
    "name": "LVA",
    "value": 99.9731
  },
  {
    "name": "LBN",
    "value": 89.9923
  },
  {
    "name": "LSO",
    "value": 105.8455
  },
  {
    "name": "LBR",
    "value": 91.59
  },
  {
    "name": "LIE",
    "value": 102.2556
  },
  {
    "name": "LTU",
    "value": 102.6071
  },
  {
    "name": "LUX",
    "value": 97.3323
  },
  {
    "name": "MAC",
    "value": 96.3242
  },
  {
    "name": "MKD",
    "value": 89.6473
  },
  {
    "name": "MDG",
    "value": 146.542
  },
  {
    "name": "MWI",
    "value": 147.9642
  },
  {
    "name": "MYS",
    "value": 102.905
  },
  {
    "name": "MLI",
    "value": 72.977
  },
  {
    "name": "MLT",
    "value": 102.7591
  },
  {
    "name": "MRT",
    "value": 100.6721
  },
  {
    "name": "MUS",
    "value": 103.7294
  },
  {
    "name": "MEX",
    "value": 103.1544
  },
  {
    "name": "FSM",
    "value": 97.1805
  },
  {
    "name": "MDA",
    "value": 92.8593
  },
  {
    "name": "MNG",
    "value": 100.6383
  },
  {
    "name": "MAR",
    "value": 113.3955
  },
  {
    "name": "MOZ",
    "value": 100.2787
  },
  {
    "name": "MMR",
    "value": 98.2936
  },
  {
    "name": "NRU",
    "value": 100.4011
  },
  {
    "name": "NPL",
    "value": 140.6295
  },
  {
    "name": "NLD",
    "value": 104.095
  },
  {
    "name": "NZL",
    "value": 98.4593
  },
  {
    "name": "NER",
    "value": 65.0248
  },
  {
    "name": "NOR",
    "value": 100.1206
  },
  {
    "name": "OMN",
    "value": 114.0607
  },
  {
    "name": "PAK",
    "value": 85.8102
  },
  {
    "name": "PLW",
    "value": 111.791
  },
  {
    "name": "PAN",
    "value": 100.8738
  },
  {
    "name": "PER",
    "value": 101.4283
  },
  {
    "name": "POL",
    "value": 100.6509
  },
  {
    "name": "PRT",
    "value": 106.1384
  },
  {
    "name": "PRI",
    "value": 90.4305
  },
  {
    "name": "QAT",
    "value": 100.7764
  },
  {
    "name": "RUS",
    "value": 98.9205
  },
  {
    "name": "RWA",
    "value": 135.1156
  },
  {
    "name": "WSM",
    "value": 106.2645
  },
  {
    "name": "STP",
    "value": 109.4119
  },
  {
    "name": "SAU",
    "value": 108.2517
  },
  {
    "name": "SEN",
    "value": 84.3095
  },
  {
    "name": "SRB",
    "value": 101.3633
  },
  {
    "name": "SYC",
    "value": 104.7033
  },
  {
    "name": "SVK",
    "value": 100.3733
  },
  {
    "name": "SVN",
    "value": 99.3749
  },
  {
    "name": "SLB",
    "value": 112.103
  },
  {
    "name": "ZAF",
    "value": 97.2689
  },
  {
    "name": "ESP",
    "value": 105.2732
  },
  {
    "name": "LKA",
    "value": 100.1062
  },
  {
    "name": "KNA",
    "value": 84.4902
  },
  {
    "name": "VCT",
    "value": 103.0432
  },
  {
    "name": "SUR",
    "value": 118.2731
  },
  {
    "name": "SWZ",
    "value": 107.951
  },
  {
    "name": "SWE",
    "value": 124.2636
  },
  {
    "name": "CHE",
    "value": 103.2725
  },
  {
    "name": "TJK",
    "value": 97.1398
  },
  {
    "name": "TZA",
    "value": 84.6786
  },
  {
    "name": "THA",
    "value": 104.0782
  },
  {
    "name": "TLS",
    "value": 136.047
  },
  {
    "name": "TGO",
    "value": 121.4028
  },
  {
    "name": "TON",
    "value": 107.465
  },
  {
    "name": "TUN",
    "value": 111.3951
  },
  {
    "name": "TUR",
    "value": 105.6009
  },
  {
    "name": "TKM",
    "value": 88.6385
  },
  {
    "name": "TUV",
    "value": 102.1212
  },
  {
    "name": "UKR",
    "value": 105.0629
  },
  {
    "name": "ARE",
    "value": 107.1077
  },
  {
    "name": "GBR",
    "value": 108.0794
  },
  {
    "name": "USA",
    "value": 99.2292
  },
  {
    "name": "URY",
    "value": 107.2961
  },
  {
    "name": "UZB",
    "value": 98.9494
  },
  {
    "name": "VEN",
    "value": 99.6989
  },
  {
    "name": "VNM",
    "value": 108.6183
  },
  {
    "name": "PSE",
    "value": 94.567
  }
];

async function renderMapChart(data, colorPalette) {
    let topology = await fetch('https://code.highcharts.com/mapdata/custom/world.topo.json')
        .then(response => response.json());

    Highcharts.mapChart('primary-container', {
        chart: {
            map: topology
        },
        title: {
            text: 'Gross Enrolment Ratio in Primary Education (Female)',
            align: 'left'
        },
        credits: {
            href: '',
            text: ''
        },
        mapNavigation: {
            enabled: true,
            buttonOptions: {
                verticalAlign: 'bottom'
            }
        },
        colorAxis: {
            min: 0,
            max: 100,
            type: 'linear',
            stops: colorPalette
        },
        series: [{
            name: 'Gross Enrolment Ratio',
            joinBy: ['iso-a3', 'name'],
            data: data,
            dataLabels: {
                enabled: true,
                format: '{point.value:.1f}',
                style: {
                    fontWeight: 'normal'
                }
            }
        }]
    });
}

renderMapChart(data1, colorPalette);
```

<figure>
  <div id="primary-container" style="width: 100%; height: 500px;"></div>
  <figcaption>These plots show the Gross Enrollment Ratio per education level around the world. Only the values collected by the World Bank are being displayed. Countries that did not share information do not display any values. Note that because of the way data is collected,  small discrepancies in the reported age of children may occasionally cause net enrollment rates to exceed 100 percent by the World Bank. However, this allows us to visualize high vs low enrollment and contrast regions of interest.</figcaption>
</figure>

## Secondary Ed.

<figure>
  <div id="secondary-container" style="width: 100%; height: 500px;"></div>
  <figcaption>These plots show the Gross Enrollment Ratio per education level around the world. Only the values collected by the World Bank are being displayed. Countries that did not share information do not display any values. Note that because of the way data is collected,  small discrepancies in the reported age of children may occasionally cause net enrollment rates to exceed 100 percent by the World Bank. However, this allows us to visualize high vs low enrollment and contrast regions of interest.</figcaption>
</figure>

```{ojs}
(async () => {
    let topology = await fetch('https://code.highcharts.com/mapdata/custom/world.topo.json')
       .then(response => response.json());

    // Data appears to be a constant structure so it can be declared with 'const'
    let data2 = [
  {
    "name": "ARB",
    "value": 67.9689
  },
  {
    "name": "EAS",
    "value": 88.3206
  },
  {
    "name": "EAP",
    "value": 86.9022
  },
  {
    "name": "EMU",
    "value": 110.7075
  },
  {
    "name": "ECS",
    "value": 105.389
  },
  {
    "name": "ECA",
    "value": 97.3475
  },
  {
    "name": "EUU",
    "value": 112.6944
  },
  {
    "name": "HPC",
    "value": 35.621
  },
  {
    "name": "HIC",
    "value": 106.1772
  },
  {
    "name": "LCN",
    "value": 97.2036
  },
  {
    "name": "LAC",
    "value": 97.1722
  },
  {
    "name": "LDC",
    "value": 40.0149
  },
  {
    "name": "LMY",
    "value": 70.4674
  },
  {
    "name": "LIC",
    "value": 35.3647
  },
  {
    "name": "LMC",
    "value": 67.3353
  },
  {
    "name": "MEA",
    "value": 76.9069
  },
  {
    "name": "MNA",
    "value": 74.3971
  },
  {
    "name": "MIC",
    "value": 77.8225
  },
  {
    "name": "NAC",
    "value": 99.5089
  },
  {
    "name": "OED",
    "value": 104.3177
  },
  {
    "name": "SAS",
    "value": 64.4181
  },
  {
    "name": "SSF",
    "value": 39.5397
  },
  {
    "name": "SSA",
    "value": 39.5373
  },
  {
    "name": "UMC",
    "value": 95.6858
  },
  {
    "name": "WLD",
    "value": 76.0124
  },
  {
    "name": "AFG",
    "value": 39.6748
  },
  {
    "name": "ALB",
    "value": 92.6062
  },
  {
    "name": "ATG",
    "value": 102.8447
  },
  {
    "name": "ARG",
    "value": 110.3069
  },
  {
    "name": "AUS",
    "value": 133.6293
  },
  {
    "name": "AUT",
    "value": 96.9263
  },
  {
    "name": "BHR",
    "value": 99.3264
  },
  {
    "name": "BRB",
    "value": 110.681
  },
  {
    "name": "BLR",
    "value": 106.099
  },
  {
    "name": "BEL",
    "value": 175.3805
  },
  {
    "name": "BLZ",
    "value": 81.706
  },
  {
    "name": "BEN",
    "value": 43.8578
  },
  {
    "name": "BMU",
    "value": 77.4333
  },
  {
    "name": "BTN",
    "value": 87.0563
  },
  {
    "name": "BOL",
    "value": 84.9471
  },
  {
    "name": "BRA",
    "value": 105.7857
  },
  {
    "name": "BRN",
    "value": 99.1009
  },
  {
    "name": "BGR",
    "value": 99.0442
  },
  {
    "name": "BFA",
    "value": 28.2284
  },
  {
    "name": "BDI",
    "value": 34.8233
  },
  {
    "name": "CPV",
    "value": 98.5005
  },
  {
    "name": "CMR",
    "value": 51.8602
  },
  {
    "name": "CHL",
    "value": 101.2064
  },
  {
    "name": "CHN",
    "value": 95.4449
  },
  {
    "name": "COL",
    "value": 102.6041
  },
  {
    "name": "COM",
    "value": 62.3779
  },
  {
    "name": "COD",
    "value": 33.3291
  },
  {
    "name": "CRI",
    "value": 123.6083
  },
  {
    "name": "CIV",
    "value": 33.1844
  },
  {
    "name": "HRV",
    "value": 100.8856
  },
  {
    "name": "CUB",
    "value": 101.4099
  },
  {
    "name": "CYP",
    "value": 99.4557
  },
  {
    "name": "CZE",
    "value": 105.3879
  },
  {
    "name": "DNK",
    "value": 132.1924
  },
  {
    "name": "DJI",
    "value": 41.4593
  },
  {
    "name": "DOM",
    "value": 82.3859
  },
  {
    "name": "ECU",
    "value": 106.5813
  },
  {
    "name": "EGY",
    "value": 85.8612
  },
  {
    "name": "SLV",
    "value": 81.3212
  },
  {
    "name": "ERI",
    "value": 31.256
  },
  {
    "name": "EST",
    "value": 110.0609
  },
  {
    "name": "FIN",
    "value": 152.1228
  },
  {
    "name": "FRA",
    "value": 111.2346
  },
  {
    "name": "GEO",
    "value": 99.6031
  },
  {
    "name": "DEU",
    "value": 99.5183
  },
  {
    "name": "GHA",
    "value": 56.0564
  },
  {
    "name": "GRC",
    "value": 103.3957
  },
  {
    "name": "GRD",
    "value": 100.5079
  },
  {
    "name": "GTM",
    "value": 61.5023
  },
  {
    "name": "GIN",
    "value": 30.6916
  },
  {
    "name": "HND",
    "value": 73.7329
  },
  {
    "name": "HKG",
    "value": 98.6149
  },
  {
    "name": "HUN",
    "value": 107.1067
  },
  {
    "name": "IND",
    "value": 74.7918
  },
  {
    "name": "IDN",
    "value": 82.1618
  },
  {
    "name": "IRN",
    "value": 87.9024
  },
  {
    "name": "IRL",
    "value": 128.6722
  },
  {
    "name": "ISR",
    "value": 102.6643
  },
  {
    "name": "ITA",
    "value": 101.4576
  },
  {
    "name": "JAM",
    "value": 86.3304
  },
  {
    "name": "JPN",
    "value": 101.9092
  },
  {
    "name": "JOR",
    "value": 84.8077
  },
  {
    "name": "KAZ",
    "value": 106.8409
  },
  {
    "name": "KOR",
    "value": 97.9589
  },
  {
    "name": "KWT",
    "value": 98.9087
  },
  {
    "name": "KGZ",
    "value": 91.1788
  },
  {
    "name": "LAO",
    "value": 54.5729
  },
  {
    "name": "LVA",
    "value": 114.0094
  },
  {
    "name": "LBN",
    "value": 61.8202
  },
  {
    "name": "LSO",
    "value": 60.4161
  },
  {
    "name": "LBR",
    "value": 33.1167
  },
  {
    "name": "LIE",
    "value": 103.2742
  },
  {
    "name": "LTU",
    "value": 104.617
  },
  {
    "name": "LUX",
    "value": 103.4755
  },
  {
    "name": "MAC",
    "value": 95.0437
  },
  {
    "name": "MKD",
    "value": 77.0836
  },
  {
    "name": "MDG",
    "value": 38.0608
  },
  {
    "name": "MWI",
    "value": 37.5407
  },
  {
    "name": "MYS",
    "value": 80.6655
  },
  {
    "name": "MLI",
    "value": 37.3652
  },
  {
    "name": "MLT",
    "value": 96.4711
  },
  {
    "name": "MRT",
    "value": 28.5849
  },
  {
    "name": "MUS",
    "value": 98.9862
  },
  {
    "name": "MEX",
    "value": 93.4649
  },
  {
    "name": "MDA",
    "value": 87.8893
  },
  {
    "name": "MOZ",
    "value": 30.5309
  },
  {
    "name": "MMR",
    "value": 51.9519
  },
  {
    "name": "NRU",
    "value": 83.4437
  },
  {
    "name": "NPL",
    "value": 68.8987
  },
  {
    "name": "NZL",
    "value": 120.9874
  },
  {
    "name": "NER",
    "value": 15.5587
  },
  {
    "name": "NOR",
    "value": 110.6189
  },
  {
    "name": "PAK",
    "value": 36.606
  },
  {
    "name": "PLW",
    "value": 116.9367
  },
  {
    "name": "PAN",
    "value": 78.3069
  },
  {
    "name": "PER",
    "value": 95.502
  },
  {
    "name": "POL",
    "value": 106.0829
  },
  {
    "name": "PRT",
    "value": 114.9665
  },
  {
    "name": "PRI",
    "value": 83.9338
  },
  {
    "name": "QAT",
    "value": 100.5274
  },
  {
    "name": "ROU",
    "value": 94.2833
  },
  {
    "name": "RUS",
    "value": 99.5336
  },
  {
    "name": "RWA",
    "value": 40.8854
  },
  {
    "name": "WSM",
    "value": 92.1822
  },
  {
    "name": "STP",
    "value": 80.4445
  },
  {
    "name": "SAU",
    "value": 93.7468
  },
  {
    "name": "SRB",
    "value": 95.4097
  },
  {
    "name": "SYC",
    "value": 81.1022
  },
  {
    "name": "SVK",
    "value": 92.3471
  },
  {
    "name": "SVN",
    "value": 110.5333
  },
  {
    "name": "ZAF",
    "value": 111.5194
  },
  {
    "name": "ESP",
    "value": 130.4096
  },
  {
    "name": "KNA",
    "value": 92.7512
  },
  {
    "name": "LCA",
    "value": 86.2007
  },
  {
    "name": "VCT",
    "value": 103.1762
  },
  {
    "name": "SUR",
    "value": 88.6371
  },
  {
    "name": "SWZ",
    "value": 65.8041
  },
  {
    "name": "SWE",
    "value": 141.5963
  },
  {
    "name": "CHE",
    "value": 98.2076
  },
  {
    "name": "THA",
    "value": 130.0553
  },
  {
    "name": "TLS",
    "value": 75.973
  },
  {
    "name": "TON",
    "value": 94.221
  },
  {
    "name": "TUR",
    "value": 101.1408
  },
  {
    "name": "TKM",
    "value": 83.7067
  },
  {
    "name": "TUV",
    "value": 90.2128
  },
  {
    "name": "UKR",
    "value": 98.2202
  },
  {
    "name": "GBR",
    "value": 130.4024
  },
  {
    "name": "USA",
    "value": 98.4728
  },
  {
    "name": "URY",
    "value": 99.996
  },
  {
    "name": "UZB",
    "value": 95.5688
  },
  {
    "name": "VEN",
    "value": 95.0397
  },
  {
    "name": "PSE",
    "value": 86.1715
  }
];

 // Initialize the map chart with the topology and data
Highcharts.mapChart(document.getElementById('secondary-container'), {
chart: {
map: topology
},
title: {
text: 'Gross Enrolment Ratio in Secondary Education (Female)',
align: 'left'
},
credits: {
href: '',
text: ''
},
mapNavigation: {
enabled: true,
buttonOptions: {
verticalAlign: 'bottom'
}
},
colorAxis: {
    min: 0,
    max: 100,
    type: 'linear',
    stops: colorPalette
  },
series: [{
  name: 'Gross Enrolment Ratio',
  joinBy: ['iso-a3', 'name'],
  data: data2,
  dataLabels: {
    enabled: true,
    format: '{point.value:.1f}',
    style: {
      fontWeight: 'normal'
    }
  }
}]
});
})();
```

## Tertiary Ed.
```{ojs}
(async () => {
    let topology = await fetch('https://code.highcharts.com/mapdata/custom/world.topo.json')
       .then(response => response.json());

    // Data appears to be a constant structure so it can be declared with 'const'
    let data3 = [
  {
    "name": "ARB",
    "value": 28.768
  },
  {
    "name": "EAS",
    "value": 41.4262
  },
  {
    "name": "EAP",
    "value": 39.1341
  },
  {
    "name": "EMU",
    "value": 76.299
  },
  {
    "name": "ECS",
    "value": 69.8713
  },
  {
    "name": "ECA",
    "value": 64.5301
  },
  {
    "name": "EUU",
    "value": 74.8719
  },
  {
    "name": "HPC",
    "value": 6.233
  },
  {
    "name": "HIC",
    "value": 81.3627
  },
  {
    "name": "LCN",
    "value": 50.4229
  },
  {
    "name": "LAC",
    "value": 48.967
  },
  {
    "name": "LDC",
    "value": 7.2776
  },
  {
    "name": "LMY",
    "value": 30.0104
  },
  {
    "name": "LIC",
    "value": 5.3644
  },
  {
    "name": "LMC",
    "value": 23.0272
  },
  {
    "name": "MEA",
    "value": 38.2514
  },
  {
    "name": "MNA",
    "value": 36.1012
  },
  {
    "name": "MIC",
    "value": 34.0113
  },
  {
    "name": "NAC",
    "value": 97.5233
  },
  {
    "name": "OED",
    "value": 75.5335
  },
  {
    "name": "SAS",
    "value": 19.9473
  },
  {
    "name": "SSF",
    "value": 7.2428
  },
  {
    "name": "SSA",
    "value": 7.2426
  },
  {
    "name": "UMC",
    "value": 48.2362
  },
  {
    "name": "WLD",
    "value": 36.904
  },
  {
    "name": "AFG",
    "value": 3.6733
  },
  {
    "name": "ALB",
    "value": 73.827
  },
  {
    "name": "DZA",
    "value": 41.9319
  },
  {
    "name": "ARG",
    "value": 102.8994
  },
  {
    "name": "ARM",
    "value": 48.4957
  },
  {
    "name": "ABW",
    "value": 23.0432
  },
  {
    "name": "AUS",
    "value": 106.3088
  },
  {
    "name": "AUT",
    "value": 87.602
  },
  {
    "name": "AZE",
    "value": 24.7532
  },
  {
    "name": "BHR",
    "value": 57.6057
  },
  {
    "name": "BGD",
    "value": 11.3874
  },
  {
    "name": "BLR",
    "value": 101.9697
  },
  {
    "name": "BEL",
    "value": 83.3614
  },
  {
    "name": "BMU",
    "value": 36.0804
  },
  {
    "name": "BWA",
    "value": 27.8302
  },
  {
    "name": "BRA",
    "value": 56.7165
  },
  {
    "name": "BRN",
    "value": 40.1249
  },
  {
    "name": "BGR",
    "value": 78.9854
  },
  {
    "name": "BDI",
    "value": 2.4079
  },
  {
    "name": "CPV",
    "value": 26.752
  },
  {
    "name": "CMR",
    "value": 14.0186
  },
  {
    "name": "TCD",
    "value": 1.133
  },
  {
    "name": "CHL",
    "value": 92.2786
  },
  {
    "name": "CHN",
    "value": 42.5336
  },
  {
    "name": "COL",
    "value": 57.1454
  },
  {
    "name": "COM",
    "value": 7.9895
  },
  {
    "name": "CRI",
    "value": 58.7833
  },
  {
    "name": "CIV",
    "value": 6.3929
  },
  {
    "name": "HRV",
    "value": 80.7207
  },
  {
    "name": "CYP",
    "value": 62.5988
  },
  {
    "name": "CZE",
    "value": 77.3893
  },
  {
    "name": "DNK",
    "value": 95.3878
  },
  {
    "name": "DOM",
    "value": 58.839
  },
  {
    "name": "EGY",
    "value": 29.9151
  },
  {
    "name": "SLV",
    "value": 30.1207
  },
  {
    "name": "ERI",
    "value": 1.6987
  },
  {
    "name": "EST",
    "value": 86.7456
  },
  {
    "name": "ETH",
    "value": 5.2668
  },
  {
    "name": "FIN",
    "value": 97.1937
  },
  {
    "name": "FRA",
    "value": 71.0006
  },
  {
    "name": "GEO",
    "value": 43.6902
  },
  {
    "name": "DEU",
    "value": 63.2546
  },
  {
    "name": "GHA",
    "value": 12.6413
  },
  {
    "name": "GRC",
    "value": 113.7101
  },
  {
    "name": "GIN",
    "value": 6.68
  },
  {
    "name": "HND",
    "value": 24.3899
  },
  {
    "name": "HKG",
    "value": 73.7638
  },
  {
    "name": "HUN",
    "value": 60.0327
  },
  {
    "name": "IND",
    "value": 25.3059
  },
  {
    "name": "IDN",
    "value": 32.8157
  },
  {
    "name": "IRN",
    "value": 63.6432
  },
  {
    "name": "IRL",
    "value": 80.3093
  },
  {
    "name": "ISR",
    "value": 76.1696
  },
  {
    "name": "ITA",
    "value": 73.4761
  },
  {
    "name": "JPN",
    "value": 60.8813
  },
  {
    "name": "KAZ",
    "value": 54.169
  },
  {
    "name": "KOR",
    "value": 80.6135
  },
  {
    "name": "KGZ",
    "value": 52.08
  },
  {
    "name": "LAO",
    "value": 16.6891
  },
  {
    "name": "LVA",
    "value": 79.2217
  },
  {
    "name": "LBN",
    "value": 45.7461
  },
  {
    "name": "LSO",
    "value": 11.6922
  },
  {
    "name": "LIE",
    "value": 24.1411
  },
  {
    "name": "LTU",
    "value": 82.0082
  },
  {
    "name": "MAC",
    "value": 78.6494
  },
  {
    "name": "MKD",
    "value": 44.2541
  },
  {
    "name": "MDG",
    "value": 4.5715
  },
  {
    "name": "MYS",
    "value": 33.1642
  },
  {
    "name": "MDV",
    "value": 20.2525
  },
  {
    "name": "MLT",
    "value": 50.8826
  },
  {
    "name": "MUS",
    "value": 42.6936
  },
  {
    "name": "MEX",
    "value": 30.0302
  },
  {
    "name": "MDA",
    "value": 47.2774
  },
  {
    "name": "MNG",
    "value": 75.916
  },
  {
    "name": "MAR",
    "value": 24.681
  },
  {
    "name": "MOZ",
    "value": 4.9736
  },
  {
    "name": "NZL",
    "value": 94.0069
  },
  {
    "name": "NOR",
    "value": 91.3718
  },
  {
    "name": "PAK",
    "value": 10.6705
  },
  {
    "name": "PHL",
    "value": 40.2738
  },
  {
    "name": "POL",
    "value": 82.5519
  },
  {
    "name": "PRT",
    "value": 70.3753
  },
  {
    "name": "PRI",
    "value": 98.8313
  },
  {
    "name": "QAT",
    "value": 39.2326
  },
  {
    "name": "ROU",
    "value": 59.061
  },
  {
    "name": "RUS",
    "value": 86.1742
  },
  {
    "name": "RWA",
    "value": 6.8717
  },
  {
    "name": "STP",
    "value": 9.0473
  },
  {
    "name": "SAU",
    "value": 59.8529
  },
  {
    "name": "SEN",
    "value": 7.7223
  },
  {
    "name": "SRB",
    "value": 66.011
  },
  {
    "name": "SYC",
    "value": 9.3471
  },
  {
    "name": "SVK",
    "value": 64.5809
  },
  {
    "name": "SVN",
    "value": 98.4889
  },
  {
    "name": "ZAF",
    "value": 23.3078
  },
  {
    "name": "ESP",
    "value": 96.9299
  },
  {
    "name": "LKA",
    "value": 21.6925
  },
  {
    "name": "KNA",
    "value": 79.7278
  },
  {
    "name": "LCA",
    "value": 22.8565
  },
  {
    "name": "SDN",
    "value": 16.8261
  },
  {
    "name": "SWE",
    "value": 75.96
  },
  {
    "name": "CHE",
    "value": 57.7078
  },
  {
    "name": "SYR",
    "value": 44.9824
  },
  {
    "name": "TJK",
    "value": 18.4034
  },
  {
    "name": "THA",
    "value": 60.0294
  },
  {
    "name": "TGO",
    "value": 5.9446
  },
  {
    "name": "TUN",
    "value": 43.1046
  },
  {
    "name": "TUR",
    "value": 80.1422
  },
  {
    "name": "TKM",
    "value": 6.1999
  },
  {
    "name": "UGA",
    "value": 4.1609
  },
  {
    "name": "UKR",
    "value": 88.4045
  },
  {
    "name": "GBR",
    "value": 64.1236
  },
  {
    "name": "USA",
    "value": 100.702
  },
  {
    "name": "UZB",
    "value": 6.4973
  },
  {
    "name": "VNM",
    "value": 31.2313
  },
  {
    "name": "PSE",
    "value": 53.7615
  }
];

 // Initialize the map chart with the topology and data
Highcharts.mapChart(document.getElementById('tertiary-container'), {
chart: {
map: topology
},
title: {
text: 'Gross Enrolment Ratio in Tertiary Education (Female)',
align: 'left'
},
credits: {
href: '',
text: ''
},
mapNavigation: {
enabled: true,
buttonOptions: {
verticalAlign: 'bottom'
}
},
colorAxis: {
    min: 0,
    max: 100,
    type: 'linear',
    stops: colorPalette
  },
series: [{
  name: 'Gross Enrolment Ratio',
  joinBy: ['iso-a3', 'name'],
  data: data3,
  dataLabels: {
    enabled: true,
    format: '{point.value:.1f}',
    style: {
      fontWeight: 'normal'
    }
  }
}]
});
})();
```

<figure>
  <div id="tertiary-container" style="width: 100%; height: 500px;"></div>
  <figcaption>These plots show the Gross Enrollment Ratio per education level around the world. Only the values collected by the World Bank are being displayed. Countries that did not share information do not display any values. Note that because of the way data is collected,  small discrepancies in the reported age of children may occasionally cause net enrollment rates to exceed 100 percent by the World Bank. However, this allows us to visualize high vs low enrollment and contrast regions of interest.</figcaption>
</figure>

:::