---
title: "Split Packed Bubble Plot"
author: "Jorge Bris Moreno"
format:
  html:
    embed-resources: true
    toc: true
editor_options:
  chunk_output_type: console
execute:
  echo: false
--- 

```{r, echo=FALSE, results='asis', runtime="js"}
# data from here: https://ourworldindata.org/grapher/world-regions-according-to-the-world-bank?tab=table

# Calling highcharts
cat('
<script src="https://code.highcharts.com/maps/highmaps.js"></script>
<script src="https://code.highcharts.com/maps/modules/exporting.js"></script>
<script src="https://code.highcharts.com/maps/modules/accessibility.js"></script>
')
```

```{r, message=FALSE, warning=FALSE, eval=FALSE}
# libraries
library(dplyr)
library(jsonlite)

# Load the data
data <- read.csv("Jorge/data/world-regions-according-to-the-world-bank.csv")

# select only columns of interest Code and `World Region according to the World Bank``
data <- data %>% select(Code, World.Region.according.to.the.World.Bank)
data <- data %>% rename(name = Code, value = World.Region.according.to.the.World.Bank)

# change regions to region numbers
data$value[data$value == "South Asia"] <- 1
data$value[data$value == "Europe and Central Asia"] <- 2
data$value[data$value == "Latin America and Caribbean"] <- 3
data$value[data$value == "Middle East and North Africa"] <- 4
data$value[data$value == "East Asia and Pacific"] <- 5
data$value[data$value == "Sub-Saharan Africa"] <- 6
data$value[data$value == "North America"] <- 7

# value to numeric
data$value <- as.numeric(data$value)

# save into json pretty
writeLines(toJSON(data, pretty = TRUE), "Jorge/data/regions.json")
```

```{ojs}
(async () => {
    // Fetch the topology data for the world map
    let topology = await fetch('https://code.highcharts.com/mapdata/custom/world.topo.json')
        .then(response => response.json());

    // Data appears to be a constant structure so it can be declared with 'const'
    let regions = [
  {
    "name": "AFG",
    "value": 1
  },
  {
    "name": "ALB",
    "value": 2
  },
  {
    "name": "DZA",
    "value": 4
  },
  {
    "name": "ASM",
    "value": 5
  },
  {
    "name": "AND",
    "value": 2
  },
  {
    "name": "AGO",
    "value": 6
  },
  {
    "name": "ATG",
    "value": 3
  },
  {
    "name": "ARG",
    "value": 3
  },
  {
    "name": "ARM",
    "value": 2
  },
  {
    "name": "ABW",
    "value": 3
  },
  {
    "name": "AUS",
    "value": 5
  },
  {
    "name": "AUT",
    "value": 2
  },
  {
    "name": "AZE",
    "value": 2
  },
  {
    "name": "BHS",
    "value": 3
  },
  {
    "name": "BHR",
    "value": 4
  },
  {
    "name": "BGD",
    "value": 1
  },
  {
    "name": "BRB",
    "value": 3
  },
  {
    "name": "BLR",
    "value": 2
  },
  {
    "name": "BEL",
    "value": 2
  },
  {
    "name": "BLZ",
    "value": 3
  },
  {
    "name": "BEN",
    "value": 6
  },
  {
    "name": "BMU",
    "value": 7
  },
  {
    "name": "BTN",
    "value": 1
  },
  {
    "name": "BOL",
    "value": 3
  },
  {
    "name": "BIH",
    "value": 2
  },
  {
    "name": "BWA",
    "value": 6
  },
  {
    "name": "BRA",
    "value": 3
  },
  {
    "name": "VGB",
    "value": 3
  },
  {
    "name": "BRN",
    "value": 5
  },
  {
    "name": "BGR",
    "value": 2
  },
  {
    "name": "BFA",
    "value": 6
  },
  {
    "name": "BDI",
    "value": 6
  },
  {
    "name": "KHM",
    "value": 5
  },
  {
    "name": "CMR",
    "value": 6
  },
  {
    "name": "CAN",
    "value": 7
  },
  {
    "name": "CPV",
    "value": 6
  },
  {
    "name": "CYM",
    "value": 3
  },
  {
    "name": "CAF",
    "value": 6
  },
  {
    "name": "TCD",
    "value": 6
  },
  {
    "name": "OWID_CIS",
    "value": 2
  },
  {
    "name": "CHL",
    "value": 3
  },
  {
    "name": "CHN",
    "value": 5
  },
  {
    "name": "COL",
    "value": 3
  },
  {
    "name": "COM",
    "value": 6
  },
  {
    "name": "COG",
    "value": 6
  },
  {
    "name": "CRI",
    "value": 3
  },
  {
    "name": "CIV",
    "value": 6
  },
  {
    "name": "HRV",
    "value": 2
  },
  {
    "name": "CUB",
    "value": 3
  },
  {
    "name": "CUW",
    "value": 3
  },
  {
    "name": "CYP",
    "value": 2
  },
  {
    "name": "CZE",
    "value": 2
  },
  {
    "name": "COD",
    "value": 6
  },
  {
    "name": "DNK",
    "value": 2
  },
  {
    "name": "DJI",
    "value": 4
  },
  {
    "name": "DMA",
    "value": 3
  },
  {
    "name": "DOM",
    "value": 3
  },
  {
    "name": "TLS",
    "value": 5
  },
  {
    "name": "ECU",
    "value": 3
  },
  {
    "name": "EGY",
    "value": 4
  },
  {
    "name": "SLV",
    "value": 3
  },
  {
    "name": "GNQ",
    "value": 6
  },
  {
    "name": "ERI",
    "value": 6
  },
  {
    "name": "EST",
    "value": 2
  },
  {
    "name": "SWZ",
    "value": 6
  },
  {
    "name": "ETH",
    "value": 6
  },
  {
    "name": "FRO",
    "value": 2
  },
  {
    "name": "FJI",
    "value": 5
  },
  {
    "name": "FIN",
    "value": 2
  },
  {
    "name": "FRA",
    "value": 2
  },
  {
    "name": "PYF",
    "value": 5
  },
  {
    "name": "GAB",
    "value": 6
  },
  {
    "name": "GMB",
    "value": 6
  },
  {
    "name": "GEO",
    "value": 2
  },
  {
    "name": "DEU",
    "value": 2
  },
  {
    "name": "GHA",
    "value": 6
  },
  {
    "name": "GIB",
    "value": 2
  },
  {
    "name": "GRC",
    "value": 2
  },
  {
    "name": "GRL",
    "value": 2
  },
  {
    "name": "GRD",
    "value": 3
  },
  {
    "name": "GUM",
    "value": 5
  },
  {
    "name": "GTM",
    "value": 3
  },
  {
    "name": "GIN",
    "value": 6
  },
  {
    "name": "GNB",
    "value": 6
  },
  {
    "name": "GUY",
    "value": 3
  },
  {
    "name": "HTI",
    "value": 3
  },
  {
    "name": "HND",
    "value": 3
  },
  {
    "name": "HKG",
    "value": 5
  },
  {
    "name": "HUN",
    "value": 2
  },
  {
    "name": "ISL",
    "value": 2
  },
  {
    "name": "IND",
    "value": 1
  },
  {
    "name": "IDN",
    "value": 5
  },
  {
    "name": "IRN",
    "value": 4
  },
  {
    "name": "IRQ",
    "value": 4
  },
  {
    "name": "IRL",
    "value": 2
  },
  {
    "name": "IMN",
    "value": 2
  },
  {
    "name": "ISR",
    "value": 4
  },
  {
    "name": "ITA",
    "value": 2
  },
  {
    "name": "JAM",
    "value": 3
  },
  {
    "name": "JPN",
    "value": 5
  },
  {
    "name": "JOR",
    "value": 4
  },
  {
    "name": "KAZ",
    "value": 2
  },
  {
    "name": "KEN",
    "value": 6
  },
  {
    "name": "KIR",
    "value": 5
  },
  {
    "name": "OWID_KOS",
    "value": 2
  },
  {
    "name": "KWT",
    "value": 4
  },
  {
    "name": "KGZ",
    "value": 2
  },
  {
    "name": "LAO",
    "value": 5
  },
  {
    "name": "LVA",
    "value": 2
  },
  {
    "name": "LBN",
    "value": 4
  },
  {
    "name": "LSO",
    "value": 6
  },
  {
    "name": "LBR",
    "value": 6
  },
  {
    "name": "LBY",
    "value": 4
  },
  {
    "name": "LIE",
    "value": 2
  },
  {
    "name": "LTU",
    "value": 2
  },
  {
    "name": "LUX",
    "value": 2
  },
  {
    "name": "MAC",
    "value": 5
  },
  {
    "name": "MDG",
    "value": 6
  },
  {
    "name": "MWI",
    "value": 6
  },
  {
    "name": "MYS",
    "value": 5
  },
  {
    "name": "MDV",
    "value": 1
  },
  {
    "name": "MLI",
    "value": 6
  },
  {
    "name": "MLT",
    "value": 4
  },
  {
    "name": "MHL",
    "value": 5
  },
  {
    "name": "MRT",
    "value": 6
  },
  {
    "name": "MUS",
    "value": 6
  },
  {
    "name": "MEX",
    "value": 3
  },
  {
    "name": "",
    "value": 5
  },
  {
    "name": "MDA",
    "value": 2
  },
  {
    "name": "MCO",
    "value": 2
  },
  {
    "name": "MNG",
    "value": 5
  },
  {
    "name": "MNE",
    "value": 2
  },
  {
    "name": "MAR",
    "value": 4
  },
  {
    "name": "MOZ",
    "value": 6
  },
  {
    "name": "MMR",
    "value": 5
  },
  {
    "name": "NAM",
    "value": 6
  },
  {
    "name": "NRU",
    "value": 5
  },
  {
    "name": "NPL",
    "value": 1
  },
  {
    "name": "NLD",
    "value": 2
  },
  {
    "name": "NCL",
    "value": 5
  },
  {
    "name": "NZL",
    "value": 5
  },
  {
    "name": "NIC",
    "value": 3
  },
  {
    "name": "NER",
    "value": 6
  },
  {
    "name": "NGA",
    "value": 6
  },
  {
    "name": "PRK",
    "value": 5
  },
  {
    "name": "MKD",
    "value": 2
  },
  {
    "name": "MNP",
    "value": 5
  },
  {
    "name": "NOR",
    "value": 2
  },
  {
    "name": "OMN",
    "value": 4
  },
  {
    "name": "PAK",
    "value": 1
  },
  {
    "name": "PLW",
    "value": 5
  },
  {
    "name": "PSE",
    "value": 4
  },
  {
    "name": "PAN",
    "value": 3
  },
  {
    "name": "PNG",
    "value": 5
  },
  {
    "name": "PRY",
    "value": 3
  },
  {
    "name": "PER",
    "value": 3
  },
  {
    "name": "PHL",
    "value": 5
  },
  {
    "name": "POL",
    "value": 2
  },
  {
    "name": "PRT",
    "value": 2
  },
  {
    "name": "PRI",
    "value": 3
  },
  {
    "name": "QAT",
    "value": 4
  },
  {
    "name": "ROU",
    "value": 2
  },
  {
    "name": "RUS",
    "value": 2
  },
  {
    "name": "RWA",
    "value": 6
  },
  {
    "name": "KNA",
    "value": 3
  },
  {
    "name": "LCA",
    "value": 3
  },
  {
    "name": "MAF",
    "value": 3
  },
  {
    "name": "VCT",
    "value": 3
  },
  {
    "name": "WSM",
    "value": 5
  },
  {
    "name": "SMR",
    "value": 2
  },
  {
    "name": "STP",
    "value": 6
  },
  {
    "name": "SAU",
    "value": 4
  },
  {
    "name": "SEN",
    "value": 6
  },
  {
    "name": "SRB",
    "value": 2
  },
  {
    "name": "SYC",
    "value": 6
  },
  {
    "name": "SLE",
    "value": 6
  },
  {
    "name": "SGP",
    "value": 5
  },
  {
    "name": "SXM",
    "value": 3
  },
  {
    "name": "SVK",
    "value": 2
  },
  {
    "name": "SVN",
    "value": 2
  },
  {
    "name": "SLB",
    "value": 5
  },
  {
    "name": "SOM",
    "value": 6
  },
  {
    "name": "ZAF",
    "value": 6
  },
  {
    "name": "KOR",
    "value": 5
  },
  {
    "name": "SSD",
    "value": 6
  },
  {
    "name": "ESP",
    "value": 2
  },
  {
    "name": "LKA",
    "value": 1
  },
  {
    "name": "SDN",
    "value": 6
  },
  {
    "name": "SUR",
    "value": 3
  },
  {
    "name": "SWE",
    "value": 2
  },
  {
    "name": "CHE",
    "value": 2
  },
  {
    "name": "SYR",
    "value": 4
  },
  {
    "name": "TJK",
    "value": 2
  },
  {
    "name": "TZA",
    "value": 6
  },
  {
    "name": "THA",
    "value": 5
  },
  {
    "name": "TGO",
    "value": 6
  },
  {
    "name": "TON",
    "value": 5
  },
  {
    "name": "TTO",
    "value": 3
  },
  {
    "name": "TUN",
    "value": 4
  },
  {
    "name": "TUR",
    "value": 2
  },
  {
    "name": "TKM",
    "value": 2
  },
  {
    "name": "TCA",
    "value": 3
  },
  {
    "name": "TUV",
    "value": 5
  },
  {
    "name": "UGA",
    "value": 6
  },
  {
    "name": "UKR",
    "value": 2
  },
  {
    "name": "ARE",
    "value": 4
  },
  {
    "name": "GBR",
    "value": 2
  },
  {
    "name": "USA",
    "value": 7
  },
  {
    "name": "VIR",
    "value": 3
  },
  {
    "name": "URY",
    "value": 3
  },
  {
    "name": "UZB",
    "value": 2
  },
  {
    "name": "VUT",
    "value": 5
  },
  {
    "name": "VEN",
    "value": 3
  },
  {
    "name": "VNM",
    "value": 5
  },
  {
    "name": "YEM",
    "value": 4
  },
  {
    "name": "ZMB",
    "value": 6
  },
  {
    "name": "ZWE",
    "value": 6
  }
];

    Highcharts.mapChart('container1', {
        chart: {
            map: topology
        },
        title: {
            text: 'Gross Enrolment Ratio in Secondary Education (Female)',
            align: 'left'
        },
        credits: {
            href: '',
            text: ''
        },
        mapNavigation: {
            enabled: true,
            buttonOptions: {
                verticalAlign: 'bottom'
            }
        },
        colorAxis: {
    dataClasses: [{
        from: 1,
        to: 2,
        color: '#3d6469',
        name: 'South Asia (1)'
    }, {
        from: 2,
        to: 3,
        color: '#ffa205',
        name: 'Europe & Central Asia (2)'
    }, {
        from: 3,
        to: 4,
        color: '#ff4500',
        name: 'Latin America & Caribbean (3)'
    }, {
        from: 4,
        to: 5,
        color: '#08030a',
        name: 'Middle East & North Africa (4)'
    }, {
        from: 5,
        to: 6,
color: '#feeece',
        name: 'East Asia & Pacific (5)'
    }, {
        from: 6,
        to: 7,
        color: '#d40637',
        name: 'Sub-Saharan Africa (6)'
    }, {
        from: 7,
        to: 8,
        color: '#5f0922',
        name: 'North America (7)'
    }]
        },
        series: [{
            name: 'Gross Enrolment Ratio',
            joinBy: ['iso-a3', 'name'],
            data: regions,
            dataLabels: {
                enabled: true,
                format: '{point.name}: {point.value}',
                style: {
                    fontWeight: 'normal'
                }
            }
        }]
    });
})();
```

<figure>
  <div id="container1" style="width: 100%; height: 500px;"></div>
  <figcaption>These plots show the Gross Enrollment Ratio per education level around the world. Only the values collected by the World Bank are being displayed. Countries that did not share information do not display any values. Note that because of the way data is collected,  small discrepancies in the reported age of children may occasionally cause net enrollment rates to exceed 100 percent by the World Bank. However, this allows us to visualize high vs low enrollment and contrast regions of interest.</figcaption>
</figure>